### 2019-09-30 nodalida-talk/talk.tex
additions

   \begin{lingex}
  	\item
  	\label{ex:acda}
  	\textbf{P1}	The inhabitants of Cambridge voted for a Labour MP.\\
  	\textbf{P2}	Every inhabitant of Cambridge voted for a Labour MP.\\
  	\textbf{H} Every inhabitant of Cambridge voted for a Labour MP.	\\ \textbf{Label:	UNK} [FraCas 094]
  \end{lingex}
    \item A syntactic conjunction of individuals is treated as a
      semantic group, or where precise counting of the members of a
      group is necessary.
    \end{itemize}\end{itemize}

@@

\begin{frame}
  \frametitle{Future Work}
  \begin{itemize}
    \item Improve support for group readings.
    % \item Improvement at the GF level: make the abstract syntax more compatible with compositional semantics
    \item Address the last section of FraCaS test suite (it contains
      many \textit{adhoc} cases, and much preliminary work to do to
      define general approach.)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Conclusions}
  \begin{itemize}
  \item We have connected two well-defined systems based on
    type-theory
    \begin{itemize}
    \item Combines the strengths of 3 systems: GF (Parsing), Haskell
      (dynamic semantics), and Coq (powerful reasoning mechanisms).
    \item Providing resource semantics for GF
    \end{itemize}

@@

  \item Hybrid NLI systems
  \item The system can be found here:  \href{https://github.com/GU-CLASP/FraCoq}{https://github.com/GU-CLASP/FraCoq}
  \end{itemize}
\end{frame}

>>>>

   \begin{lingex}
  	\item
  	\label{ex:acda}
  	\textbf{P1}	The inhabitants of Cambridge voted for a Labour MP.\\
  	\textbf{H} Every inhabitant of Cambridge voted for a Labour MP.	\\ \textbf{Label:	UNK} [FraCas 094]
  \end{lingex}

    \end{itemize}\end{itemize}

@@

\begin{itemize}
	\item Group readings

	\begin{itemize}

		\item A syntactic conjunction of individuals is treated as a
	semantic group, or where precise counting of the members of a
	group is necessary.

	\end{itemize}

		\begin{lingex}
			\item
			\label{ex:acda}
			\textbf{P1}		Smith signed one contract.\\
						\textbf{P2}		Jones signed another contract.\
			\textbf{H} Smith and Jones signed two contracts.\\ \textbf{Label:	YES, on a collective reading of the sentence} [FraCas 111]
		\end{lingex}

\end{itemize}

\begin{frame}
  \frametitle{Future Work}
  \begin{itemize}
    \item Improve support for group readings
    % \item Improvement at the GF level: make the abstract syntax more compatible with compositional semantics
    \item Address the  section of  the FraCaS test suite  left, i.e. section 7: Temporal reference (tense and aspect)

     \begin{itemize}
    	\item  Contains
      many \textit{adhoc} cases, and much preliminary work is needed in order to
      define general approach
  \end{itemize}  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Conclusions}
  \begin{itemize}
  \item We have connected three well-defined systems based on
    type-theory
    \begin{itemize}
    \item Combines the strengths of 3 systems: GF (Parsing), Haskell
      (dynamic semantics), and Coq (powerful reasoning mechanisms).
    \item Providing resource semantics for GF
    \end{itemize}

@@

  \item Hybrid NLI systems?
  \item The system can be found here:  \href{https://github.com/GU-CLASP/FraCoq}{https://github.com/GU-CLASP/FraCoq}
  \end{itemize}
\end{frame}
